Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-02-28 eg6-letters/incoherent/incoherent_prl.tex
minor edit to fix implementing the first suggestion from stepan regarding the PID paragraph

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state using the standard particle identification 
Note that even though the DVCS reaction has only one real photon in the final 
state, events with more than one photon were not discarded at this stage. These 
extra photons were mostly soft photons from accidental coincidence which, as 
will be discussed below, the DVCS exclusivity cuts easily eliminated.  In the 
following selection stage, the most energetic photon was considered as the DVCS 
photon candidate.

>>>>

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state using the standard particle identification 
framework of the CLAS event reconstruction (see \cite{Hattawy:thesis} for 
additional details on the particle identification). Note that even though the 
DVCS reaction has only one real photon in the final state, events with more 
than one photon were not discarded at this stage. These extra photons were 
mostly soft photons from accidental coincidence which, as will be discussed 
below, the DVCS exclusivity cuts easily eliminated.  In the following selection 
stage, the most energetic photon was considered as the DVCS photon candidate.
